---
title: "ccs_stations"
author: "Aaron Shavitz"
format: 
  html:
    code-fold: true
    code-summary: "Show the code"
    fig-format: png
    fig-dpi: 300
    
execute:
  dev: ragg_png
  fig-width: 6.5
  fig-height: 4
---
[Return to Home Page (Index)](https://ashavitz.github.io/wellfleet_project/)

# CCS Water Quality Data - Wellfleet

```{r, echo=FALSE}
# Using knitr package to read code chunks from ccs_stations.R

# Set the root directory to the current folder
knitr::opts_knit$set(root.dir = here::here())

# Read in the R script from the 'scripts' folder (relative to the root project directory)
knitr::read_chunk("../scripts/ccs_stations.R")
```

```{r Header}
```

### Load Libraries
```{r Load Libraries, message=FALSE, warning=FALSE}
```

### Set Global ggplot Themes
```{r Set Global ggplot Themes, message=FALSE, warning=FALSE}
```

### Read CCS csv data
```{r csv import from CCS, message=FALSE, warning=FALSE}
```

### Filter Only "Full" Years With at Least One Monthly Measurement
```{r Filter Only "Full" Years With at Least One Monthly Measurement}
```

### Filter Only "Full" Summers With at Least One Monthly Measurement June - September
```{r Filter Only "Full" Summers With at Least One Monthly Measurement June - September}
```

### Filter Only "Full" Springs With at Least One Monthly Measurement March - June
```{r Filter Only "Full" Springs With at Least One Monthly Measurement March - June}
```

### Filter Only "Full" Autumns With at Least One Monthly Measurement October - December
```{r Filter Only "Full" Autumns With at Least One Monthly Measurement October - December}
```

### Log10 Transform Variables
```{r Log10 Transform Variables, message=FALSE, warning=FALSE}
```

### Create metadata variables for labeling
```{r Create metadata variables for labeling, message=FALSE, warning=FALSE}
```

### Simple Linear Models - Monthly
```{r Simple Linear Models - Monthly, message=FALSE, warning=FALSE}
```

### Plot All Data (~Monthly)
```{r Plot All Data, message=FALSE, warning=FALSE}
```

### Plot Annual Mean and Median
```{r Plot Annual Mean and Median, message=FALSE, warning=FALSE}
```

### Plot All Summer Data (~Monthly, summer only)
```{r Plot All Summer Data, message=FALSE, warning=FALSE}
```

### Plot Summer Mean
```{r Plot Summer Mean, message=FALSE, warning=FALSE}
```

### Plot Spring Mean
```{r Plot Spring Mean, message=FALSE, warning=FALSE}
```

### Plot Autumn Mean
```{r Plot Autumn Mean, message=FALSE, warning=FALSE}
```

### Plots for Final Report
```{r Plots for Final Report, message=FALSE, warning=FALSE, fig.width=13, fig.height=4}
```


